QRF Covariate Selection

### 2020-02-05 analysis/R_scripts/fit_qrf_model.Rmd
changed a few selected habitat metrics, added things to the habitat dictionary, re-ran fit_qrf_model.Rmd script.

@@

```{r load-data}
# determine which set of fish/habitat data to use
data("fh_sum_champ_2017")
fish_hab = fh_sum_champ_2017 %>%
  filter(Species == 'Chinook') %>%
  mutate_at(vars(Watershed, Year),
            list(as.factor))

@@

# all the related habitat data
data("champ_site_2011_17")
hab_data = champ_site_2011_17 %>%
  filter(!Watershed %in% c('Big-Navarro-Garcia (CA)',
                           'CHaMP Training',
                           'Region 17',
                           'Walla Walla',
                           'Umatilla'))

data("champ_site_2011_17_avg")
hab_avg = champ_site_2011_17_avg %>%
  filter(!Watershed %in% c('Big-Navarro-Garcia (CA)',
                           'CHaMP Training',
                           'Region 17',
                           'Walla Walla',
                           'Umatilla'))

@@

@@

mine_res = fish_hab %>%
  mutate_at(vars(starts_with('LWVol')),
            list(~ . / Lgth_Wet)) %>%
  mutate(fish_dens = log(fish_dens + 0.005)) %>%
  estimate_MIC(covars = poss_hab_mets,
               response = 'fish_dens') %>%
  mutate(Species = 'Chinook') %>%
  left_join(hab_dict %>%
              filter(MetricGroupName == 'Visit Metric') %>%
              select(Metric = ShortName,
                     MetricCategory,
                     Name),
            by = 'Metric') %>%
  mutate_at(vars(MetricCategory),
            list(fct_explicit_na),
            na_level = 'Other') %>%
  mutate_at(vars(Name),
            list(as.character)) %>%
  mutate(Name = if_else(is.na(Name),
                        as.character(Metric),
                        Name)) %>%
  # put the metric names in descending order by MIC
  mutate_at(vars(Metric, Name),
            list(~ fct_reorder(., .x = MIC))) %>%
  select(Species, MetricCategory, Metric, everything()) %>%
  arrange(Species, MetricCategory, desc(MIC))

@@

```{r habitat-covariates}
sel_hab_mets = tibble(Species = c('Chinook'),
                      Metric = c("WetWDRat_Avg",
                                 "CU_Freq",
                                 "DpthWet_SD",
                                 "WetBraid",
                                 "FishCovTotal",
                                 "RipCovUstory",
                                 'WetWdth_Int',
                                 'Q',
                                 "SubLT6",
                                 "SubD16",
                                 "avg_aug_temp",
                                 "LWFreq_Wet"))
                      # 
                      # Metric = c('UcutArea_Pct',
                      #            'FishCovNone',
                      #            'SubEstGrvl',
                      #            'FstTurb_Freq',
                      #            'FstNT_Freq',
                      #            'CU_Freq',
                      #            'SlowWater_Pct',
                      #            'NatPrin1',
                      #            'DistPrin1',
                      #            'avg_aug_temp',
                      #            # 'Sin_CL',
                      #            'Sin',
                      #            'WetWdth_CV',
                      #            'WetBraid',
                      #            'WetSC_Pct',
                      #            'Q',
                      #            'WetWdth_Int',
                      #            'LWFreq_Wet',
                      #            'LWVol_WetFstTurb'))

>>>>

# Load Data

@@

```{r load-data}
# determine which set of fish/habitat data to use
data("fh_sum_champ_2017")
fish_hab = fh_sum_champ_2017 %>%
  filter(Species == 'Chinook') %>%
  mutate_at(vars(Watershed, Year),
            list(as.factor)) %>%
  # scale some metrics by site length
  mutate_at(vars(starts_with('LWVol')),
            list(~ . / Lgth_Wet * 100)) %>%
  mutate(RipCovCanSome = 100 - RipCovCanNone)

@@

# change some of the descriptions for large wood volume
hab_dict %<>%
  mutate(DescriptiveText = if_else(grepl("^LWVol", ShortName),
                                   paste0(str_remove(DescriptiveText, ".$"),
                                         ", scaled by site length."),
                                   DescriptiveText),
         UnitOfMeasure = if_else(grepl("^LWVol", ShortName),
                                   paste0(UnitOfMeasure,
                                         " per 100 meters"),
                                   UnitOfMeasure),
         UnitOfMeasureAbbrv = if_else(grepl("^LWVol", ShortName),
                                   paste0(UnitOfMeasureAbbrv,
                                         "/100m"),
                                   UnitOfMeasureAbbrv)) %>%
  bind_rows(hab_dict_2017 %>%
              filter(ShortName == "RipCovCanNone") %>%
              mutate(ShortName = "RipCovCanSome",
                     Name = "Riparian Cover: Some Canopy",
                     DescriptiveText = "Percent of riparian canopy with some vegetation."))

# all the related habitat data
data("champ_site_2011_17")
hab_data = champ_site_2011_17 %>%
  filter(!Watershed %in% c('Big-Navarro-Garcia (CA)',
                           'CHaMP Training',
                           'Region 17',
                           'Walla Walla',
                           'Umatilla')) %>%
  mutate(RipCovCanSome = 100 - RipCovCanNone)

data("champ_site_2011_17_avg")
hab_avg = champ_site_2011_17_avg %>%
  filter(!Watershed %in% c('Big-Navarro-Garcia (CA)',
                           'CHaMP Training',
                           'Region 17',
                           'Walla Walla',
                           'Umatilla')) %>%
  mutate(RipCovCanSome = 100 - RipCovCanNone)

@@

## MINE Statistics

@@

mine_res = fish_hab %>%
  mutate(fish_dens = log(fish_dens + 0.005)) %>%
  estimate_MIC(covars = poss_hab_mets,
               response = 'fish_dens') %>%
  mutate(Species = 'Chinook') %>%
  left_join(hab_dict %>%
              filter(MetricGroupName == 'Visit Metric') %>%
              select(Metric = ShortName,
                     MetricCategory,
                     Name),
            by = 'Metric') %>%
  mutate_at(vars(MetricCategory),
            list(fct_explicit_na),
            na_level = 'Other') %>%
  mutate_at(vars(Name),
            list(as.character)) %>%
  mutate(Name = if_else(is.na(Name),
                        as.character(Metric),
                        Name)) %>%
  # put the metric names in descending order by MIC
  mutate_at(vars(Metric, Name),
            list(~ fct_reorder(., .x = MIC))) %>%
  select(Species, MetricCategory, Metric, everything()) %>%
  arrange(Species, MetricCategory, desc(MIC))

@@

```{r habitat-covariates}
sel_hab_mets = tibble(Species = c('Chinook'),
                      Metric = c("WetWDRat_Avg",
                                 "CU_Freq",
                                 "DpthWet_SD",
                                 "WetBraid",
                                 "FishCovTotal",
                                 # "RipCovUstory",
                                 # "RipCovBigTree",
                                 "RipCovCanSome",
                                 'WetWdth_Int',
                                 'Q',
                                 "SubLT6",
                                 "SubD16",
                                 "avg_aug_temp",
                                 "LWVol_WetSlow"))
                                 # "LWFreq_Wet"))
                      # 
                      # Metric = c('UcutArea_Pct',
                      #            'FishCovNone',
                      #            'SubEstGrvl',
                      #            'FstTurb_Freq',
                      #            'FstNT_Freq',
                      #            'CU_Freq',
                      #            'SlowWater_Pct',
                      #            'NatPrin1',
                      #            'DistPrin1',
                      #            'avg_aug_temp',
                      #            # 'Sin_CL',
                      #            'Sin',
                      #            'WetWdth_CV',
                      #            'WetBraid',
                      #            'WetSC_Pct',
                      #            'Q',
                      #            'WetWdth_Int',
                      #            'LWFreq_Wet',
                      #            'LWVol_WetFstTurb'))
